Figures

### 2020-04-30 PPP/Figures.Rmd

```{r}
## load library
library(greta)

@@

>>>>

```{r, eval = FALSE}
## load library
library(greta)

@@

```{r}
typical_df <- tibble(x = seq(-4,4,length.out = 100), d_norm =  dnorm(x))

typical_df %>% ggplot(aes(x,d_norm)) + 
  annotate("rect", xmin=-1.7, xmax=1.7, ymin=0, ymax=Inf, alpha = 0.5) +
  # geom_rect(aes(xmin=-1.7, xmax=1.7, ymin=0, ymax=Inf), alpha = 0.3, fill = "gray") +
  geom_line(size = 2) + 
  theme_minimal() + 
  theme(
    axis.title = element_blank(),
    axis.text = element_blank()
  ) + 
  xlab(expression(pi*"("*theta*")"*" "*d*theta))
